---
title: "Homework 3 2018"
author: "Irene Yang"
date: "2/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following is documentation that I have installed and loaded the necessary packages and files for class on 2/28.  

1. Document that you have installed `dada2` and `phyloseq`, as well as `shortread` and `ggplot2`. 

```{r HW3Q1}

# First make sure you have the latest version of R and Bioconductor, then install the current release of dada2 (packageVersion 1.6.0), phyloseq (packageVersion 1.22.3), and ShortRead (packageVersion 1.36.1) from bioconductor

source("https://bioconductor.org/biocLite.R")
biocLite("dada2")
biocLite("phyloseq")
biocLite("ShortRead")

# If you already have these packages, load them
library(dada2); packageVersion("dada2")
library(phyloseq); packageVersion("phyloseq")
library(ShortRead); packageVersion("ShortRead")

#Also load ggplot2 (packageVersion 2.2.1)
library(ggplot2); packageVersion("ggplot2")
```

2. Please document that you have downloaded THREE additional files as follows: 
* fastq files from the Mothur MiseqSOP walkthrough
* RDP training set
* RDP species assignment set

```{r H3Q2}

path <- "~/Desktop/N741/2018week6/MiSeq_SOP"
fns <- list.files(path)

fns

path2 <- "~/Desktop/N741/2018week6/RDP Data"
fns2 <- list.files(path2)

fns2
```

